\cvsection{Education}
\begin{cventries}
    \cventry
        {MEng Engineering Science - Classification: 2.i.}
        {The University of Oxford}
        {St. Catherine's College}
        {Sep. 2013 - Jun. 2017}
        {
          \begin{_cvitems}
            \item{Co-authored a paper relating to the findings of my fourth year project, `Mosquito Detection with Neural Networks: The Buzz of Deep Learning'.}
            \item{Awarded the Gibb's prize for best third year team project. Designed hardware, a distributed computing facility, and set of computational processes that make it possible to scan, process, upload, and save an entire human brain for possible future reanimation. This fine-tuned my team working skills and has broadened my data analysis skill-set.}
            \item{\textit{Key Modules:} Machine Vision \& Robotics~~·~~Machine Learning~~·~~Medical Imaging \& Informatics~~·~~Probability, Systems \& Perturbation Methods~~·~~Nonlinear \& Predictive Control~~·~~Software Engineering~~·~~Information Engineering~~·~~Biomedical Modelling \& Monitoring.}
          \end{_cvitems}
        }
    \cventry
        {}
        {Queen Elizabeth High School}
        {Hexham}
        {Sep. 2008 - Jun. 2013}
        {\vspace{-0.5cm}
          \begin{_cvitems}
            \item {\textit{A-Levels:} \textbf{A${^*}$} Maths~~·~~\textbf{A${^*}$} Further Maths~~·~~\textbf{A${^*}$} Physics~~·~~\textbf{A} Product Design~~·~~\textbf{A} Extended Project}
            \item {\textit{GCSEs:} \textbf{6A${^*}$}s~~·~~\textbf{5A}s} 
          \end{_cvitems}
        }

\end{cventries}
