\cvsection{Education}
\begin{cventries}
    \cventry
        {MEng Engineering Science - 2.i.}
        {The University of Oxford}
        {St. Catherine's College}
        {Sep. 2013 - Jun. 2017}
        {
            \begin{cvitems}
                \item{Awarded the Gibb's prize for best third year team project. Designed hardware, a distributed computing facility, and set of computational processes that make it possible to scan, process, upload, and save an entire human brain for possible future reanimation. This fine-tuned my team working skills and has broadened my data analysis skill-set.}
                \item{Co-authored a paper relating to the findings of my fourth year project, `Mosquito Detection with Neural Networks: The Buzz of Deep Learning'.}
                \item{Key Modules: Machine Vision \& Robotics · Machine Learning · Medical Imaging \& Informatics · Probability, Systems \& Perturbation Methods · Nonlinear \& Predictive Control · Software Engineering · Information Engineering · Biomedical Modelling \& Monitoring.}
            \end{cvitems}
        }
    \cventry
        {}
        {Queen Elizabeth High School}
        {Hexham, UK}
        {Sep. 2008 - Jun. 2013}
        {
            \begin{cvitems}
                \item{\textit{A-Levels:} \textbf{A${{^*}}$} Maths~~·~~\textbf{A${{^*}}$} Further Maths~~·~~\textbf{A${{^*}}$} Physics~~·~~\textbf{A} Product Design~~·~~\textbf{A} Extended Project}
                \item{\textit{GCSEs:} \textbf{6A${{^*}}$}s~~·~~\textbf{5A}s}
            \end{cvitems}
        }

\end{cventries}